### 2016-06-13 sec4_baseline.tex
Some updates
On sec4

The work flow of TRM is illustrate as in Figure~\ref{fig:trm}. 
In brief, there are two pipeline MR jobs which further consist of four stages. 
The first MR job is considered as a preprocessing, where input trajectories
are grouped into snapshots and each snapshot runs a clustering method (e.g., Disk-based, DBSCAN, etc.).
The output is shown as in Figure~\ref{fig:trm}(b). The second
MR job is the \emph{TRM} algorithm. In the \emph{map} phase 
(i.e., Figure~\ref{fig:trm} (c)), temporally closed snapshots are grouped
into a partition. In the \emph{reduce} phase (i.e., Figure~\ref{fig:trm} (d)),
a \emph{Line Sweeping} method is developed to discover GCMP in each partition. Finally,
patterns from different partitions are then collected to form the output.

@@

Since in the first MR job, each partition contains only one snapshot
for clustering, it is not necessary to replicate any snapshot. Thus, we
focus on describing the second MR job which is the \emph{Temporal
Replication and Mining} algorithm. We use $R$ to denote the replication factor.
The outline of TRM is 
shown in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $R \gets (\lceil \frac{K}{L} \rceil -1)*G+2K-2$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...R$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$
\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
three steps. First, in the map phase, each snapshot is keyed 
with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
Second, in the partition phase, every snapshot is grouped with its next 
$R$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
We will shortly discuss how the $R$ value is derived. 
Third, in the reduce phase, a line sweeping method is invoked 
to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $R$ times.
%\subsubsection{Temporal Replication Partition}
The replication factor $R$ is critical for the performance of TRM.
If the $R$ is large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if $R$ is small, valid patterns may
be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
$R$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K-2$. We will show
later the correctness of this value.

@@

\subsection{Line Sweep Mining}
Each task in the reduce phase processes a partition $Par_i$, which contains
$R$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
only the patterns whose object sets are contained in the first snapshot 
are necessary to be reported. Therefore, we design a simple 
\emph{line-sweep mining}(LSM) method for discovering
GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.

@@

\subsection{Correctness of TRM}
We prove the correctness of TRM from three aspects. First,
setting $R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$
would not miss any valid patterns. Second, no false patterns
are reported in any partitions. Third, the choice of $R$ is
minimum. We formalize the first two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
\end{definition}

Apparently, in TRM, replicating the entire trajectories (i.e., $R=\mathbb{|T|}$)
meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We prove in the following theorem 
that the minimum $R$ is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$ 
to ensure the correctness:

@@

\begin{theorem}[Correctness of Temporal Replication]
\label{thm:replication_partition}
The minimum $R$ to ensure sound and complete of the temporal replication 
is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
\end{theorem}z
\begin{proof}
The soundness of partition can be observed from the fact 
that each partition represents a consecutive segments of trajectories. 
Therefore patterns in a partition can be directly mapped 
back to original trajectories. 
For completeness, let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
of a valid sequence $T$. Let $R$ be the upper bound for all $T'$s among 
all possible valid sequence. It is easy to see that, under such a setting,
any valid sequence would be captured by one of the partitions in temporal
replication. This proves the completeness. Now, we compute the minimum value
of $R$ as follows:
$T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Therefore $R$ is formulated 
as follows:
\begin{equation}
R = \max_{n} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
\end{equation}
With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
Observe that, constraints (1)-(4) form a convex polygon and $R$ is monotone
increasing wrt. $n$, the maximum value of $R$ is thus taken at the boundaries. Further
observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
conditions naturally derive
$R = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
%with the smallest length. Note that there could be many qualified $T'$s. 
%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
%If every partition is of at least such a size, then $T'$ must be
%captured by at least one of the partition. Thus, the pattern $P$ would 
%be valid in that partition. This proves the completeness.
\end{proof}

\begin{example}
We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=3, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K - 2 = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $4$, since the timestamps of $\{o_1,o_2\}$ and $\{o_5,o_6\}$ 
are both $\{1,2\}$ which violate the $G$ constraint, 
thus the two candidates are removed from $C_4$. After all snapshots are swept, 
$\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

The TRM approach though achieves good parallelism, 
it requires to replicate the data multiple times. 
Specifically, each snapshots are replicate $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
Handling those cases is equivalent to replicate the entire snapshots to each partition, 
which surrenders the benefit of parallelism.

>>>>

The work flow of TRM is illustrate as in Figure~\ref{fig:trm}. 
In brief, there are two pipeline MR jobs which further consist of four stages. 
The first MR job is considered as a preprocessing, where input trajectories
are grouped into snapshots and each snapshot runs a clustering method (e.g., Disk-based, DBSCAN, etc.).
The output is shown as in Figure~\ref{fig:trm}(b). The second
MR job is the \emph{TRM} algorithm. In the \emph{map} phase 
(i.e., Figure~\ref{fig:trm} (c)), temporally closed snapshots are grouped
into a partition. In the \emph{reduce} phase (i.e., Figure~\ref{fig:trm} (d)),
a \emph{Line Sweeping} method is developed to discover GCMP in each partition. Finally,
patterns from different partitions are then collected to form the final output.

@@

In the first MR job, each partition contains only one snapshot
for clustering, thus it is unnecessary to replicate any snapshots. Therefore, we
focus on describing the second MR job which is the \emph{Temporal
Replication and Mining} algorithm. We use $\eta$ to denote the replication factor.
The outline of TRM is 
shown in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*G+2K-2$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...R$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$
\State where $Par_t = \{S_t, S_{t+1}, .. S_{t+R}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
three steps. First, in the map phase, each snapshot is keyed 
with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
Second, in the partition phase, every snapshot is grouped with its next 
$\eta$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). 
Third, in the reduce phase, a line sweeping method is invoked 
to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $\eta$ times.
The replication factor $\eta$ is critical for the performance of TRM.
If the $\eta$ is large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if $\eta$ is small, valid patterns may
be missed out. In the Algorithm~\ref{algo:trm_overview}, the 
$\eta$ is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K-2$. We will shortly show that this is the minimum $\eta$ to guarantee the correctness.

@@

\subsection{Line Sweep Mining}
Each task in the reduce phase processes a partition $Par_i$, which contains
$\eta$ snapshots starting from snapshot $S_i$. We observe that within each $Par_i$, 
only the patterns whose object sets are contained in the first snapshot are necessary to be reported. Therefore, we design a simple 
\emph{line-sweep mining}(LSM) method for discovering
GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.

@@

\subsection{Correctness of TRM}
We prove the correctness of TRM in three aspects. First,
setting $\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$
would not miss any valid patterns. Second, no false patterns
are reported in any partitions. Third, the choice of $\eta$ is
minimum. We formalize the first two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions a trajectory database $Tr$ 
into segments, $Par_1,...,Par_m$. $\mathbb{P}$ is complete 
if for every valid pattern $P$ in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. 
$\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $Tr$.
\end{definition}

Apparently, in TRM, replicating the entire trajectories (i.e., $\eta=\mathbb{|T|}$)
meets the \emph{soundness} and \emph{completeness} requirements. However, it burdens the network shuffle and limits the parallelism. We prove in the following theorem 
that the minimum $\eta$ is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$ 
to ensure the correctness:

@@

\begin{theorem}[Correctness of Temporal Replication]
\label{thm:replication_partition}
The minimum $\eta$ to ensure sound and complete of the temporal replication 
is $(\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
\end{theorem}
\begin{proof}
The soundness of partition can be observed from the fact 
that each partition represents a consecutive segments of trajectories. 
Therefore patterns in a partition can be directly mapped 
back to original trajectories. 
For completeness, let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
all possible valid sequence. It is easy to see that, under such a setting,
any valid sequence would be captured by one of the partitions in temporal
replication. This proves the completeness. Now, we compute the minimum value
of $\eta$ as follows:
any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
as follows:
\begin{equation}
\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
\end{equation}
With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
conditions naturally derive
$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
%with the smallest length. Note that there could be many qualified $T'$s. 
%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
%If every partition is of at least such a size, then $T'$ must be
%captured by at least one of the partition. Thus, the pattern $P$ would 
%be valid in that partition. This proves the completeness.
\end{proof}

\begin{example}
We illustrate the work flow of  TRM method using Figure~\ref{fig:trm} (c)(d) with $M=2, K=3, L = 2, G=2$. 
In Figure~\ref{fig:trm} (c), snapshots are combined into partitions with sizes equal to 
$(\lceil \frac{K}{L} \rceil-1) *G+2K - 2 = 4$. Then a line sweep method is performed in (d) 
for partition $1$. Each $C_i$ refers to the candidate set during sweeping snapshot $i$. 
Initially, $C_1$ contains patterns whose object set is in snapshot $1$.
As line sweeps, at snapshot $3$, since the timestamps of  $\{o_5,o_6\}$ is $\{1\}$, which violates both the $L$,and $G$ constraints, this candidate is eliminated.
At snapshot $4$, since the timestamps of $\{o_1,o_2\}$ is $\{1,2\}$, which violates the $L$ constraints, thus it is removed. Therefore, $\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

The TRM approach though achieves good parallelism, 
it requires to replicate the data $\eta$ times. 
In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $\eta$ meeds to be as large as $|\mathbb{T}|$. 
Handling those cases are equivalent to replicate the entire snapshots to each partition, 
which surrenders the benefit of parallelism.
